When two-point correlation function fails to describe a structure...

### 2024-03-07 paper.tex
Cite theorems properly

Breuillard et~al. \cite{breuillard2019irreducibility} give the following
approximation for this probability if the Riemann hypothesis holds for the
Dedekind zeta function $\zeta_K$ for all number fields of the form
$K = \mathbb{Q}(a)$, where $a$ is a root of $f$.
\begin{equation}
  P(\text{$f$ is irreducible}) = 1 - \sqrt{\frac{2}{\pi d}} + O(d^{-1})
  \label{eq:prob-irr}
\end{equation}

\textcolor{red}{How to cite a theorem in the paper?}
Another useful result is that for large enough $d$ the probability
of $f$ having factorization $\Phi \tilde{f}$ where $\tilde{f}$ is an irreducible
polynomial and $\Phi$ is a product of cyclotomic polynomials is at least
\begin{equation}
  P = 1 - 2\exp(-c(\log d)^{\beta - 2})
  \label{eq:prob-cyc-1}
\end{equation}
for some $c > 0$ and $\beta > 3$ if $\zeta_K$ has no zeros $\rho$ with
$|1 - \rho| < (\log d)^\alpha/d$, $\alpha > \beta$ for all $K = \mathbb{Q}(a)$
for any root $a$ of $f$.

>>>>

Breuillard et~al. \cite[Corollary~4]{breuillard2019irreducibility} give the
following approximation for this probability if the Riemann hypothesis holds for
the Dedekind zeta function $\zeta_K$ for all number fields of the form
$K = \mathbb{Q}(a)$, where $a$ is a root of $f$.
\begin{equation}
  P(\text{$f$ is irreducible}) = 1 - \sqrt{\frac{2}{\pi d}} + O(d^{-1})
  \label{eq:prob-irr}
\end{equation}

Another useful result is that for large enough $d$ the probability
of $f$ having factorization $\Phi \tilde{f}$ where $\tilde{f}$ is an irreducible
polynomial and $\Phi$ is a product of cyclotomic polynomials is at least
\begin{equation}
  P = 1 - 2\exp(-c(\log d)^{\beta - 2})
  \label{eq:prob-cyc-1}
\end{equation}
for some $c > 0$ and $\beta > 3$ if $\zeta_K$ has no zeros $\rho$ with
$|1 - \rho| < (\log d)^\alpha/d$, $\alpha > \beta$ for all $K = \mathbb{Q}(a)$
for any root $a$ of $f$ \cite[Theorem~5]{breuillard2019irreducibility}.
